### 2017-06-08 Latex/Introduction/presento.tex
Add itroduction presentation

\documentclass[14pt]{beamer}

% Presento style file
\usepackage{config/presento}

% custom command and packages
\input{config/custom-command}

% Information
\title{Drumtranscription}
\subtitle{Detect drums in polyphonic sound}
\author{Anyere Bendrien \\ Maximilian Wagenbach}
\institute{Audio Content Analysis \\ TU Berlin}
\date{\today}

\begin{document}
% Title page
\begin{frame}[plain]
\maketitle
\end{frame}

\notosansfont

% sections in the presentation
\begin{frame}{Drumtranscription}
 \begin{fullpageitemize}
  \item Detect percussive events in polyphonic sound
  \item Onset and Type (Bassdrum, Hi Hat, Snare, ...)

  \item \textbf{Optional:} \\
        Visualization of drum onsets
  \item Tempodetection / Beat Grid [2]
 \end{fullpageitemize}
\end{frame}

\begin{frame}{Non-negative Matrix Factorization}
 \begin{fullpageitemize}
  \item 
  \begin{figure}
   \includegraphics[width=\textwidth]{images/Flowchart.png}
   \caption{Flowchart of the drum transcription system [1]}
  \end{figure}
  \notosansfont
  \item 
 \end{fullpageitemize}
\end{frame}

\begin{frame}
 \frametitle{References}
  {\small [1] Chih-Wei Wu, Alexander Lerch. “Drum Transcription Using Partially Fixed Non-Negative Matrix Factorization with Template Adaptation”, 16th International Society for Music Information Retrieval Conference, 2015}\\
  {\small [2] Daniel Gärtner. “Tempo Detection Of Urban Music Using Tatum Grid Non-Negative Martix Factorizytion”, International Society for Music Information Retrieval, 2013}
\end{frame}

\framecard[colorgreen]{{\color{white}\hugetext{Thanks for listening!}}}

\end{document}

### 2017-08-15 Latex/Paper/main.tex
Initial latex for paper

% Template for ICASSP-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{AUTOMATED TRANSCRIPTION OF DRUMSOUNDS}
%
% Single address.
% ---------------
\name{Anyere Bendrien, Maximilian Wagenbach
    \thanks{Thanks to Holger Kirchhof and Tim Flohrer for assistance.}}
\address{Technical University of Berlin\\
    Audiocommunication Group\\
    Einsteinufer 17, 10587 Berlin}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
Non-Negative Matrixfactorization, Drums, Profit
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

These guidelines include complete descriptions of the fonts, spacing, and
related information for producing your proceedings manuscripts. Please follow
them and if you have any questions, direct them to Conference Management
Services, Inc.: Phone +1-979-846-6800 or email
to \\\texttt{papers@icassp2016.org}.

\section{Formatting your paper}
\label{sec:format}

All printed material, including text, illustrations, and charts, must be kept
within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
not write or print anything outside the print area. The top margin must be 1
inch (25 mm), except for the title page, and the left margin must be 0.75 inch
(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
fully justified.

\section{PAGE TITLE SECTION}
\label{sec:pagestyle}

The paper title (on the first page) should begin 1.38 inches (35 mm) from the
top edge of the page, centered, completely capitalized, and in Times 14-point,
boldface type.  The authors' name(s) and affiliation(s) appear below the title
in capital and lower case letters.  Papers with multiple authors and
affiliations may require two or more lines for this information. Please note
that papers should not be submitted blind; include the authors' names on the
PDF.

\section{TYPE-STYLE AND FONTS}
\label{sec:typestyle}

To achieve the best rendering both in printed proceedings and electronic proceedings, we
strongly encourage you to use Times-Roman font.  In addition, this will give
the proceedings a more uniform look.  Use a font that is no smaller than nine
point type throughout the paper, including figure captions.

In nine point type font, capital letters are 2 mm high.  {\bf If you use the
smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
vertically.}  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
the paper much more readable.  Larger type sizes require correspondingly larger
vertical spacing.  Please do not double-space your paper.  TrueType or
Postscript Type 1 fonts are preferred.

The first paragraph in each section should not be indented, but all the
following paragraphs within the section should be indented as these paragraphs
demonstrate.

\section{MAJOR HEADINGS}
\label{sec:majhead}

Major headings, for example, "1. Introduction", should appear in all capital
letters, bold face if possible, centered in the column, with one blank line
before, and one blank line after. Use a period (".") after the heading number,
not a colon.

\subsection{Subheadings}
\label{ssec:subhead}

Subheadings should appear in lower case (initial word capitalized) in
boldface.  They should start at the left margin on a separate line.

\subsubsection{Sub-subheadings}
\label{sssec:subsubhead}

Sub-subheadings, as in this paragraph, are discouraged. However, if you
must use them, they should appear in lower case (initial word
capitalized) and start at the left margin on a separate line, with paragraph
text beginning on the following line.  They should be in italics.

\section{PRINTING YOUR PAPER}
\label{sec:print}

Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
empty at the BOTTOM of the page and follow the top and left margins as
specified.  If the last page of your paper is only partially filled, arrange
the columns so that they are evenly balanced if possible, rather than having
one long column.

In LaTeX, to start a new column (but not a new page) and help balance the
last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
demonstrated on this page (see the LaTeX source below).

\section{PAGE NUMBERING}
\label{sec:page}

Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
conference identification will be inserted when the paper is included in the
proceedings.

\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
\label{sec:illust}

Illustrations must appear within the designated margins.  They may span the two
columns.  If possible, position illustrations at the top of columns, rather
than in the middle or at the bottom.  Caption and number every illustration.
All halftone illustrations must be clear black and white prints.  Colors may be
used, but they should be selected so as to be readable when printed on a
black-only printer.

Since there are many ways, often incompatible, of including images (e.g., with
experimental results) in a LaTeX document, below is an example of how to do
this \cite{Lamp86}.

\section{FOOTNOTES}
\label{sec:foot}

Use footnotes sparingly (or not at all!) and place them at the bottom of the
column on the page on which they are referenced. Use Times 9-point type,
single-spaced. To help your readers, avoid using footnotes altogether and
include necessary peripheral observations in the text (within parentheses, if
you prefer, as in this sentence).

% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------
\begin{figure}[htb]

\begin{minipage}[b]{1.0\linewidth}
  \centering
  \centerline{\includegraphics[width=8.5cm]{figures/image1}}
%  \vspace{2.0cm}
  \centerline{(a) Result 1}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{figures/image3}}
%  \vspace{1.5cm}
  \centerline{(b) Results 3}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{figures/image4}}
%  \vspace{1.5cm}
  \centerline{(c) Result 4}\medskip
\end{minipage}
%
\caption{Example of placing a figure with experimental results.}
\label{fig:res}
%
\end{figure}

% To start a new column (but not a new page) and help balance the last-page
% column length use \vfill\pagebreak.
% -------------------------------------------------------------------------
%\vfill
%\pagebreak

\section{COPYRIGHT FORMS}
\label{sec:copyright}

You must submit your fully completed, signed IEEE electronic copyright release
form when you submit your paper. We {\bf must} have this form before your paper
can be published in the proceedings.

\section{RELATION TO PRIOR WORK}
\label{sec:prior}

The text of the paper should contain discussions on how the paper's
contributions are related to prior work in the field. It is important
to put new work in  context, to give credit to foundational work, and
to provide details associated with the previous work that have appeared
in the literature. This discussion may be a separate, numbered section
or it may appear elsewhere in the body of the manuscript, but it must
be present.

You should differentiate what is new and how your work expands on
or takes a different path from the prior studies. An example might
read something to the effect: "The work presented here has focused
on the formulation of the ABC algorithm, which takes advantage of
non-uniform time-frequency domain analysis of data. The work by
Smith and Cohen \cite{Lamp86} considers only fixed time-domain analysis and
the work by Jones et al \cite{C2} takes a different approach based on
fixed frequency partitioning. While the present study is related
to recent approaches in time-frequency analysis [3-5], it capitalizes
on a new feature space, which was not considered in these earlier
studies."

\vfill\pagebreak

\section{REFERENCES}
\label{sec:refs}

List and number all bibliographical references at the end of the
paper. The references can be numbered in alphabetic order or in
order of appearance in the document. When referring to them in
the text, type the corresponding reference number in square
brackets as shown at the end of this sentence \cite{C2}. An
additional final page (the fifth page, in most cases) is
allowed, but must contain only references to the prior
literature.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{strings,refs}

\end{document}

### 2017-08-15 Latex/Paper/main.tex
Ground structure of the paper

@@
 \usepackage{spconf,amsmath,graphicx}
+\usepackage{blindtext}
 
@@
 \label{sec:intro}
+
+context, problem, use cases
+definitions
+paper overview
+
+% section intro (end)
+
+\section{Related work}
+\label{sec:rel}
+
+literature review, state of the art
+
+% section rel (end)
+
+\section{algorithm overview and description}
+\label{sec:algo}
+
+\blindtext
+
+% section algo (end)
+
+\section{Evaluation}
+\label{sec:evaluation}
+
+ground truth, methodology, metrics
+results
+discussion
+
+% section evaluation (end)
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+summary, noteworthy parts of the presented work,
+achievements and contributions
+possible improvements and future work
+
+% section conclusion (end)
+
+% References should be produced using the bibtex program from suitable
+% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
+% style file from IEEE produces unsorted bibliography list.
+% -------------------------------------------------------------------------
+\bibliographystyle{IEEEbib}
+\bibliography{strings,refs}
+
+%\end{document}
+
+% DELETE EVERYTHING FROM HERE IN THE END
+% DELETE EVERYTHING FROM HERE IN THE END
+% DELETE EVERYTHING FROM HERE IN THE END
+
+\vfill\pagebreak
+
+\section{common flaws}
+all cited papers should appear in bibliography
+vice versa: all references should be mentioned in the paper
+each reference should contain:
+names of authors
+title of the paper or book
+conference paper: name of conf. incl. year and location
+journal paper: name of journal incl. volume, year and pages
+book: publisher, potentially editor
+all figures and tables must be referenced in the paper
+equations:
+all mathematical symbols must be explained
+symbols should be used consistently and unambiguously
+abbreviations (STFT, DFT, etc.) should be introduced
+”The short-time Fourier transform (STFT) is given by (. . .)
+We compute the STFT of the signal, (. . .)”
+
+\section{Evaluation}
+
+form (structure, language, form of references)
+content (introduction, literature review, algorithm and
+evaluation description, figures, comprehensibility, correctness)
+evaluation (dataset, metrics, discussion)
+
+\vfill\pagebreak
+~
+\vfill\pagebreak
 
@@
 
-% References should be produced using the bibtex program from suitable
-% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
-% style file from IEEE produces unsorted bibliography list.
-% -------------------------------------------------------------------------
-\bibliographystyle{IEEEbib}
-\bibliography{strings,refs}
-
 \end{document}

### 2017-08-15 Projekt/main.py
Changes to the python code and added PDF pictures.

@@ -16,19 +16,21 @@ def main():
     # load the bass drum template
     fs, template = getNormalizedAudio("base_drum.wav")
 
-    # plt.plot(template)
-    # plt.axvspan(0, 1024, color='red', alpha=0.5)
-    # plt.savefig("BassdrumTemplate.pdf")
-    # plt.show()
+    plt.plot(template)
+    plt.axvspan(0, 1024, color='red', alpha=0.5)
+    plt.xlabel("Sample")
+    plt.ylabel("Amplitude")
+    plt.savefig("BassdrumTemplate.pdf")
+    plt.show()
 
     # setup the file directories
-    drummer = 2
+    drummer = 1
     audioPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/audio/wet_mix/"
     annotationPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/annotation/"
 
     # get all audio file names
-    allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
-    #allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
+    #allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
+    allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
 
     positives = []
     false_positives = []

### 2017-08-15 Latex/Paper/main.tex
Started writing. Introduction and NMF explanation.

@@
 \begin{keywords}
-Non-Negative Matrixfactorization, Drums, Profit
+Non-Negative Matrix Factorization, Drum Transcription, Profit
 \end{keywords}
@@
 \label{sec:intro}
+
+For this research paper we looked into the topic of generating a drum transcription from a piece of music containing a recording of a drum kit.
+Drum transcription is considered a classical music information retrieval (MIR) problem, where you want to extract information from a mixed piece of music.
+In order to achieve this an algorithm is applied to the raw sound data to find the time points where a drum event happens in the song.
+This list of time points and a corresponding flag with the kind of the drum event is called the drum transcription. 
+While in theory this can be used to find any kind of percussive event within a musical piece, we focused mainly on base drum hits in our research.
+
+The transcription of the drum track of a song can be useful in many cases.
+The simplest would be to generate the sheet music for a song where the original has been lost or is not available.
+It can also be used for more sophisticated use cases like a conversion of a audio file to a MIDI sequence (known as Audio-to-MIDI).
+For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also a integral part.
+Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
+For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm. [QUELLE]
+Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.
+
+On first sight extracting the time point of a drum hit for a polyphonic, mixed piece of music sounds like a difficult task.
+In fact though there are multiple mathematically simple algorithm to achieve that.
+For this research we took an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).
+NMF is in its essence a pattern matching algorithm.
+It decomposes the magnitude spectrum of a song into two matrices.
+The first one contains the magnitude spectra of the individual components and the second one contains the time-varying gain of these components, which tells us when each of the components for the first matrix is active.
+The sum of both matrices makes up an approximation of the original spectrum. \cite{virtanen2007}
 
@@
 
+The idea to use NMF for pattern recognition was first proposed by Lee and Seung in 1999 \cite{lee1999}.
+As described in their paper NMF is a versatile technique to find features in a data set.
+It can for example be used to recognize parts of a face, find semantic features in text or certain events in a piece of music.
+
 % section rel (end)
@@
 
-\blindtext
+basic NMF description, our peak picking algorithm, maybe libs used
 
@@
 experimental results) in a LaTeX document, below is an example of how to do
-this \cite{Lamp86}.
+this.
 
@@
 non-uniform time-frequency domain analysis of data. The work by
-Smith and Cohen \cite{Lamp86} considers only fixed time-domain analysis and
-the work by Jones et al \cite{C2} takes a different approach based on
+Smith and Cohen considers only fixed time-domain analysis and
+the work by Jones et al takes a different approach based on
 fixed frequency partitioning. While the present study is related
@@
 the text, type the corresponding reference number in square
-brackets as shown at the end of this sentence \cite{C2}. An
+brackets as shown at the end of this sentence. An
 additional final page (the fifth page, in most cases) is

### 2017-08-15 Latex/Paper/main.tex
Rework introduction

@@
 This list of time points and a corresponding flag with the kind of the drum event is called the drum transcription. 
-While in theory this can be used to find any kind of percussive event within a musical piece, we focused mainly on base drum hits in our research.
+While in theory this can be used to find any kind of event within a musical piece, we focused mainly on basic drum sounds in our research.
 
@@
 It can also be used for more sophisticated use cases like a conversion of a audio file to a MIDI sequence (known as Audio-to-MIDI).
-For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also a integral part.
+For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also an integral part.
 Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
-For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm. [QUELLE]
+For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm [QUELLE].
 Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.
@@
 For this research we took an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).
-NMF is in its essence a pattern matching algorithm.
-It decomposes the magnitude spectrum of a song into two matrices.
-The first one contains the magnitude spectra of the individual components and the second one contains the time-varying gain of these components, which tells us when each of the components for the first matrix is active.
-The sum of both matrices makes up an approximation of the original spectrum. \cite{virtanen2007}
+
+In section \ref{sec:algo} there will be a detailed explanation of how NMF works.
 
@@
 \label{sec:algo}
+
+NMF is in its essence a pattern matching algorithm.
+It decomposes the magnitude spectrum of a song into two matrices.
+The first one contains the magnitude spectra of the individual components we are interested in and the second one contains the time-varying gain of these components, which tells us when each of the components for the first matrix is active.
+The sum of both matrices makes up an approximation of the original spectrum. \cite{virtanen2007}
 

### 2017-08-16 Projekt/main.py
Commenting code and generalized over drummers and drumsounds

@@ -14,83 +14,102 @@ from os import path
 def main():
 
     # load the bass drum template
-    fs, template = getNormalizedAudio("base_drum.wav")
+    fs, bdTemplate = getNormalizedAudio("base_drum.wav")
 
-    plt.plot(template)
-    plt.axvspan(0, 1024, color='red', alpha=0.5)
-    plt.xlabel("Sample")
-    plt.ylabel("Amplitude")
-    plt.savefig("BassdrumTemplate.pdf")
-    plt.show()
+    # plt.plot(template)
+    # plt.axvspan(0, 1024, color='red', alpha=0.5)
+    # plt.xlabel("Sample")
+    # plt.ylabel("Amplitude")
+    # plt.savefig("BassdrumTemplate.pdf")
+    # plt.show()
 
-    # setup the file directories
-    drummer = 1
-    audioPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/audio/wet_mix/"
-    annotationPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/annotation/"
+    data = [[2, "bd", bdTemplate], [2, "chh", bdTemplate]]
+    for drummer, drumName, template in data:
 
-    # get all audio file names
-    #allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
-    allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
+        # setup the file directories
+        audioPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/audio/wet_mix/"
+        annotationPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/annotation/"
 
-    positives = []
-    false_positives = []
+        # get all audio file names
+        allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
 
-    trackNames = []
-    results = []
-    numberOfAnalyzedTracks = 0
-    for audioFile in allAudioFiles:
-        # load annotations
-        filename = path.splitext(audioFile)[0]
-        annotations = loadAnnotationFile(annotationPath + filename + ".txt", "bd")
+        print("Transcripting: " + drumName + " of drummer " + str(drummer) + "\n=============")
 
-        # check if the files contains bass drums
-        if annotations.size == 0:
-            # otherwise skip the track
-            continue
+        positives = []
+        false_positives = []
[…]

### 2017-08-16 Latex/Paper/main.tex
More infos about the structure of the paper

@@
 \begin{abstract}
-The abstract should appear at the top of the left-hand column of text, about
-0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
-length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
-beginning of the main text.  The abstract should contain about 100 to 150
-words, and should be identical to the abstract text submitted electronically
-along with the paper cover sheet.  All manuscripts must be in English, printed
-in black ink.
+Stark verkürzte, überblicksartige Darstellung von Forschungsbedarf, Fragestellung, Methode, erwartetem
+Ergebnis und Nutzen.
+The abstract should contain about 100 to 150 words.
 \end{abstract}
@@
 
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
 context, problem, use cases
@@
 paper overview
+
+Kurzes Umreißen des Themengebiets mit schneller Fokussierung auf den zu untersuchenden Gegenstand.
+Hierzu können technikhistorische Aspekte oder eine Forschungstradition skizziert, ein
+bestehender theoretischer Hintergrund erhellt, eine Einordnung in Forschungsdisziplinen vorgenommen
+und ggf. ein persönliches Forschungsinteresse dargelegt werden. Die Einführung des
+Themengebiets sollte auf eine konkrete Fragestellung zugespitzt werden, gleichzeitig soll die Relevanz
+des Themas deutlich werden, z.B. mit Hinblick auf Gesellschaft, Grundlagenforschung oder
+konkrete Anwendungen.
 
@@
 
-literature review, state of the art
-
 The idea to use NMF for pattern recognition was first proposed by Lee and Seung in 1999 \cite{lee1999}.
@@
 It can for example be used to recognize parts of a face, find semantic features in text or certain events in a piece of music.
+
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+literature review, state of the art
+
+Überblick über bestehende Arbeiten im thematisch näheren Forschungsbereich. Der Autor vermittelt
+hier zum einen seine Kenntnis der Materie und zeigt zum anderen Forschungsdefizite und ggf.
+Anknüpfungspunkte an bestehende Arbeiten auf. Daraus ergeben sich die Forschungsrelevanz,
+eine weitere thematische Eingrenzung sowie mögliche methodische Ansätze.
 
@@
 \vfill\pagebreak
+
+The abstract should appear at the top of the left-hand column of text, about
+0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
+length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
+beginning of the main text.  The abstract should contain about 100 to 150
+words, and should be identical to the abstract text submitted electronically
+along with the paper cover sheet.  All manuscripts must be in English, printed
+in black ink.
 

### 2017-08-16 Latex/Paper/main.tex
Continued writing text and made matrix plot prettier.

@@
 For this research we took an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).
-
-In section \ref{sec:algo} there will be a detailed explanation of how NMF works.
+Section \ref{sec:algo} will show a detailed explanation of how the NMF works.
 
@@
 As described in their paper NMF is a versatile technique to find features in a data set.
-It can for example be used to recognize parts of a face, find semantic features in text or certain events in a piece of music.
+Lee and Seung proposed in their paper that it can be used to recognize parts in faces, find semantic features in texts or find certain musical events in a piece of music.
+During the last decade NMF was researched and applied in all the fields they mentioned and many more.
+
+In the field of music information retrieval NMF has also been used in a variety of applications.
+Most notable are the fields of source separation and music transcription.
+For source separation the goal is to separate a piece of music containing a mix of multiple sound sources into the their components.
+Virtanen \cite{virtanen2007} has researched this topic among many others.
 
@@
 
-NMF is in its essence a pattern matching algorithm.
-It decomposes the magnitude spectrum of a song into two matrices.
-The first one contains the magnitude spectra of the individual components we are interested in and the second one contains the time-varying gain of these components, which tells us when each of the components for the first matrix is active.
-The sum of both matrices makes up an approximation of the original spectrum. \cite{virtanen2007}
+As mentioned before we used a non-negative matrix factorization to extract the time points of drum events from a drum track.
+Generally speaking the NMF factorizes a matrix (usually called $\mathbf{V}$) into two smaller matrices (usually called $\mathbf{W}$ and $\mathbf{H}$) with the constraint that every matrix element must be non-negative.
+In turn the sum of $\mathbf{W}$ and $\mathbf{H}$ is an approximation of $\mathbf{V}$ (see figure \ref{fig:NMF}).
+
+\begin{figure}[htb]
+
+\begin{minipage}[b]{1.0\linewidth}
+  \centering
+  \centerline{\includegraphics[width=8.5cm]{figures/NMF}}
+%  \vspace{2.0cm}
+  \medskip
+\end{minipage}
+
+\caption{Matrix $\mathbf{V}$ can be factorized into two matrices $\mathbf{W}$ and $\mathbf{H}$, so that their sum approximates $\mathbf{V}$. \scriptsize{\textcopyright WikiMedia CC BY-SA 3.0}}
+\label{fig:NMF}
+
+\end{figure}
+
+In our case we use the magnitude spectrum of a song as the $\mathbf{V}$ matrix and decomposed it into two matrices.
+The first one contains the magnitude spectra of the individual components we are interested in ($\mathbf{W}$) and the second one contains the time-varying gain of these components ($\mathbf{H}$), which tells us when each of the components for the first matrix is active.
+For that reason the $\mathbf{W}$ matrix is usually called component matrix and $\mathbf{H}$ is usually called activation matrix.
+Again the sum of both of these matrices makes up an approximation of the original spectrum \cite{smaragdis2003}.
+A visual representation of that can be seen in figure \ref{fig:MatrixOverview} (d).
+
+For our use case we were not interested in finding all the components and their activations.
+We were rather interested in finding the corresponding activation of a specific component, like that of a base drum or a hi-hat.
+This is also possible using NMF.
+In order to do so, we specified $\mathbf{W}$ as the spectrum of a base drum and $\mathbf{V}$ continued to be the spectrum of the whole song.
+The NMF then solves for the matrix $\mathbf{H}$ which tells at what point in time the specified base drum spectrum appears in the song.
+In that setup the NMF essentially works as a pattern matching algorithm.
+
+\begin{figure}[htb]
+
+\begin{minipage}[b]{1.0\linewidth}
+  \centering
+  \centerline{\includegraphics[width=8.5cm]{figures/MatrixOverview}}
+%  \vspace{2.0cm}
+  \medskip
+\end{minipage}
+
+\caption{(a) Magnitude spectrum of a drum track.
+(b) Magnitude spectrum of a base drum.
+(c) Activation matrix of the base drum.
+(d) Approximated spectrum.
+\scriptsize{\textcopyright Own work CC BY-SA 3.0}}
+\label{fig:MatrixOverview}
+
+\end{figure}
 
@@
 discussion
+
+- we only uses drum tracks, but it also works with mixed music. problem: ground truth
 

### 2017-08-16 Projekt/main.py

@@ -142,30 +142,37 @@ def findTemplate(audio, template, annotations, fs):
     W = lsnmf_fit.basis()
     H = lsnmf_fit.coef()
 
+    # uncomment the following block for a overview plot of the NMF matrices
+
     # f, axarr = plt.subplots(2, 2)
     # plt.subplots_adjust(hspace=0.5)
     #
     # axarr[0, 0].matshow(V, aspect='auto', origin='lower', norm=LogNorm(vmin=0.01, vmax=1))
-    # axarr[0, 0].set_title('Original spectrum')
+    # axarr[0, 0].set_title('(a) Original spectrum')
     # axarr[0, 0].xaxis.set_ticks_position('bottom')
     # #axarr[0, 0].colorbar(im, cax=axcolor, ticks=t, format='$%.2f$')
-    # print("V: " + str(V.shape))
     #
     # axarr[0, 1].matshow(W, aspect='auto', origin='lower')
-    # axarr[0, 1].set_title('W')
+    # axarr[0, 1].set_title('(b) W')
     # axarr[0, 1].xaxis.set_ticks_position('bottom')
-    # print("W: " + str(W.shape))
+    # # hacky way to get only 0 and 1 as x labels
+    # axarr[0, 1].set_xlim([0, 0.5])
+    # axarr[0, 1].set_xticklabels([0, 1], fontdict=None, minor=False)
+    # axarr[0, 1].locator_params(axis='x', nbins=2)
     #
     # axarr[1, 0].matshow(H, aspect='auto', origin='lower')
-    # axarr[1, 0].set_title('H')
+    # axarr[1, 0].set_title('(c) H')
     # axarr[1, 0].xaxis.set_ticks_position('bottom')
-    # print("H: " + str(H.shape))
+    # # hacky way to get only 0 and 1 as y labels
+    # axarr[1, 0].set_ylim([0, 0.5])
+    # axarr[1, 0].set_yticklabels([0, 1], fontdict=None, minor=False)
+    # axarr[1, 0].locator_params(axis='y', nbins=2)
     #
     # axarr[1, 1].matshow(W*H, aspect='auto', origin='lower', norm=LogNorm(vmin=0.01, vmax=1))
-    # axarr[1, 1].set_title('W*H')
+    # axarr[1, 1].set_title('(d) W*H')
     # axarr[1, 1].xaxis.set_ticks_position('bottom')
     #
-    # plt.savefig("MatrixOverview.pdf")
[…]

### 2017-08-16 Latex/Paper/main.tex
Anweisungen auskommentiert.

@@
 
-Kurzes Umreißen des Themengebiets mit schneller Fokussierung auf den zu untersuchenden Gegenstand.
-Hierzu können technikhistorische Aspekte oder eine Forschungstradition skizziert, ein
-bestehender theoretischer Hintergrund erhellt, eine Einordnung in Forschungsdisziplinen vorgenommen
-und ggf. ein persönliches Forschungsinteresse dargelegt werden. Die Einführung des
-Themengebiets sollte auf eine konkrete Fragestellung zugespitzt werden, gleichzeitig soll die Relevanz
-des Themas deutlich werden, z.B. mit Hinblick auf Gesellschaft, Grundlagenforschung oder
-konkrete Anwendungen.
+%Kurzes Umreißen des Themengebiets mit schneller Fokussierung auf den zu untersuchenden Gegenstand.
+%Hierzu können technikhistorische Aspekte oder eine Forschungstradition skizziert, ein
+%bestehender theoretischer Hintergrund erhellt, eine Einordnung in Forschungsdisziplinen vorgenommen
+%und ggf. ein persönliches Forschungsinteresse dargelegt werden. Die Einführung des
+%Themengebiets sollte auf eine konkrete Fragestellung zugespitzt werden, gleichzeitig soll die Relevanz
+%des Themas deutlich werden, z.B. mit Hinblick auf Gesellschaft, Grundlagenforschung oder
+%konkrete Anwendungen.
 
@@
 
-Überblick über bestehende Arbeiten im thematisch näheren Forschungsbereich. Der Autor vermittelt
-hier zum einen seine Kenntnis der Materie und zeigt zum anderen Forschungsdefizite und ggf.
-Anknüpfungspunkte an bestehende Arbeiten auf. Daraus ergeben sich die Forschungsrelevanz,
-eine weitere thematische Eingrenzung sowie mögliche methodische Ansätze.
+%Überblick über bestehende Arbeiten im thematisch näheren Forschungsbereich. Der Autor vermittelt
+%hier zum einen seine Kenntnis der Materie und zeigt zum anderen Forschungsdefizite und ggf.
+%Anknüpfungspunkte an bestehende Arbeiten auf. Daraus ergeben sich die Forschungsrelevanz,
+%eine weitere thematische Eingrenzung sowie mögliche methodische Ansätze.
 

### 2017-08-16 Latex/Paper/main.tex
Continued writing text about algorithm.

@@
 \usepackage{blindtext}
+\usepackage[utf8]{inputenc}
 
@@
 For source separation the goal is to separate a piece of music containing a mix of multiple sound sources into the their components.
-Virtanen \cite{virtanen2007} has researched this topic among many others.
+T. Virtanen \cite{virtanen2007} among many others has researched this topic.
+
+In the field of music transcription NMF has also been used for different topics.
+Smaragdis and Brown \cite{smaragdis2003} used NMF to analyze and extract polyphonic, harmonic content from a piece of music.
+In the sub-field of drum transcription there has also been some research in the recent years.
+Paulus and Virtanen \cite{paulus2005} as well as Moreau and Flexer \cite{moreau2007} as well as Wu and Lerch \cite{wu2015} have all shown that NMF is a technique that can be well applied to the problem of finding the time points of percussive events in music.
 
@@
 
-As mentioned before we used a non-negative matrix factorization to extract the time points of drum events from a drum track.
-Generally speaking the NMF factorizes a matrix (usually called $\mathbf{V}$) into two smaller matrices (usually called $\mathbf{W}$ and $\mathbf{H}$) with the constraint that every matrix element must be non-negative.
+As mentioned above we used a non-negative matrix factorization to extract the time points of drum events from a drum track.
+In general terms the NMF factorizes a matrix (usually called $\mathbf{V}$) into two smaller matrices (usually called $\mathbf{W}$ and $\mathbf{H}$) with the constraint that every matrix element must be non-negative.
 In turn the sum of $\mathbf{W}$ and $\mathbf{H}$ is an approximation of $\mathbf{V}$ (see figure \ref{fig:NMF}).
@@
 
-\caption{Matrix $\mathbf{V}$ can be factorized into two matrices $\mathbf{W}$ and $\mathbf{H}$, so that their sum approximates $\mathbf{V}$. \scriptsize{\textcopyright WikiMedia CC BY-SA 3.0}}
+\caption{Matrix $\mathbf{V}$ can be factorized into two matrices $\mathbf{W}$ and $\mathbf{H}$, so that their sum approximates $\mathbf{V}$.
+\scriptsize{\textsf{\textcopyright} WikiMedia CC BY-SA 3.0}}
 \label{fig:NMF}
@@
 This is also possible using NMF.
-In order to do so, we specified $\mathbf{W}$ as the spectrum of a base drum and $\mathbf{V}$ continued to be the spectrum of the whole song.
-The NMF then solves for the matrix $\mathbf{H}$ which tells at what point in time the specified base drum spectrum appears in the song.
+In order to do so, we specified $\mathbf{W}$ as the spectrum of a base drum (see figure \ref{fig:MatrixOverview} (b)) and $\mathbf{V}$ continued to be the spectrum of the whole song (see figure \ref{fig:MatrixOverview} (a)).
+The NMF then solves for the matrix $\mathbf{H}$ (see figure \ref{fig:MatrixOverview} (c)) which tells us at what point in time the specified base drum spectrum appears in the song.
 In that setup the NMF essentially works as a pattern matching algorithm.
@@
 (d) Approximated spectrum.
-\scriptsize{\textcopyright Own work CC BY-SA 3.0}}
+\scriptsize{\textsf{\textcopyright} Own work CC BY-SA 3.0}}
 \label{fig:MatrixOverview}
+
+\end{figure}
+
+\begin{figure}[htb]
+
+\begin{minipage}[b]{1.0\linewidth}
+  \centering
+  \centerline{\includegraphics[width=8.5cm]{figures/Flowchart}}
+%  \vspace{2.0cm}
+  \medskip
+\end{minipage}
+
+\caption{Flowchart of the whole drum transcription algorithm. \scriptsize{\textsf{\textcopyright} Own work CC BY-SA 3.0}}
+\label{fig:Flowchart}
+
+\end{figure}
+
+Figure \ref{fig:Flowchart} shows a flowchart with the complete overview of the algorithm we developed.
+On the left hand side the two inputs to the algorithms are shown.
+The first input is a time domain signal of percussive instrument, like a base drum or hi-hat, and the second input is a time domain signal of a piece of music.
+For both inputs the first step is to apply the short-time Fourier transform (STFT) which transforms both signal from the time domain to the frequency domain.
+For the parameters of the STFT we used a frame size of 1024 samples which yields in a frequency resolution of approx. 43 Hz per bin.
+We also chose an overlap of 50\% between hops to improve the time resolution.
+As mentioned before a visual representations of both transformed inputs can be found in figure \ref{fig:MatrixOverview} (b) and (a) respectively.
+Before both inputs together are fed into the actual detection the drum sound undergoes some further processing.
+This step is marked as template extraction in figure \ref{fig:Flowchart}.
+%% TODO: explain transient and shit
+After both inputs are prepared they are handed over to the NMF, which does its processing in the way described in the paragraph above.
+As explained the result of the NMF is in our case the activation matrix $\mathbf{H}$.
+The matrix $\mathbf{H}$ can also be viewed as a function curve of how much the given template is contribution to the given music signal over time.
+An example of the representation of the matrix $\mathbf{H}$ as a curve can be seen in figure \ref{fig:ActivationMatrix}.
+
+\begin{figure}[htb]
+
+\begin{minipage}[b]{1.0\linewidth}
+  \centering
+  \centerline{\includegraphics[width=8.5cm]{figures/ActivationMatrix}}
+%  \vspace{2.0cm}
+  \medskip
+\end{minipage}
+
+\caption{Example of the representation of an activation matrix as a curve. \scriptsize{\textsf{\textcopyright} Own work CC BY-SA 3.0}}
+\label{fig:ActivationMatrix}
+
+\end{figure}
+
+The next step of the algorithm is called onset detection where the exact time points are extracted from that curve.
+The onset detection is a simple implementation loosely based on the algorithms described by Lerch \cite{lerch2012book} in chapter 6.3.
+To extract the onsets of the drum events the significant local maxima of the curve (peaks) have to be detected.
+In order to do that the curve is first normalized.
+Afterwards a threshold of $\frac{2}{3}$ is applied.
+This value was establish empirically to separate the valid detection from false positives.
+Then the first derivative, which represents the slope of the curve, is calculated, by subtracting each element from the previous one.
+An example of the resulting curve can be found in figure \ref{fig:Ableitung}.
+
+\begin{figure}[htb]
+
+\begin{minipage}[b]{1.0\linewidth}
+  \centering
+  \centerline{\includegraphics[width=8.5cm]{figures/Ableitung}}
+%  \vspace{2.0cm}
+  \medskip
+\end{minipage}
+
+\caption{An example of the first derivative of the activation function. \scriptsize{\textsf{\textcopyright} Own work CC BY-SA 3.0}}
+\label{fig:Ableitung}
 
@@
 possible improvements and future work
+
+Improvements: 
+- Using adaptive templates like shown in \cite{lerch2015} can help the "over-fitting" of a template.
+- adaptive threshold instead of 2/3
 

### 2017-08-16 Projekt/main.py
Removed borders from graphics.

@@ -185,7 +185,7 @@ def findTemplate(audio, template, annotations, fs):
     # plt.figure()
     # plt.plot(thresholdline, color='r')
     # plt.plot(Harray)
-    # plt.savefig("ActivationMatrix.pdf")
+    # plt.savefig("ActivationMatrix.pdf", bbox_inches='tight')
     # plt.show()
 
     # apply threshold
@@ -194,7 +194,7 @@ def findTemplate(audio, template, annotations, fs):
 
     # plt.figure()
     # plt.plot(Harray)
-    # plt.savefig("ZeroCrosses.pdf")
+    # plt.savefig("ZeroCrosses.pdf", bbox_inches='tight')
     # plt.show()
 
     #Harray[Harray == 0] = np.nan

### 2017-08-17 Latex/Paper/main.tex
Removed borders from graphics.
Continued algorithm description and started evaluation.

@@
 \usepackage[utf8]{inputenc}
+\usepackage{hyperref}
 
@@
 \name{Anyere Bendrien, Maximilian Wagenbach
-    \thanks{Thanks to Holger Kirchhof and Tim Flohrer for assistance.}}
+    \thanks{Thanks to Holger Kirchhof and Tim Flohrer for assistance. Also thanks to TELECOM ParisTech - Dep. TSIe for generously providing the ENST drum test data set.}}
 \address{Technical University of Berlin\\
@@
 The first input is a time domain signal of percussive instrument, like a base drum or hi-hat, and the second input is a time domain signal of a piece of music.
-For both inputs the first step is to apply the short-time Fourier transform (STFT) which transforms both signal from the time domain to the frequency domain.
+For both inputs the first step is to down mix the signals into a mono signal.
+Next the short-time Fourier transform (STFT) is applied, which transforms both signal from the time domain to the frequency domain.
 For the parameters of the STFT we used a frame size of 1024 samples which yields in a frequency resolution of approx. 43 Hz per bin.
@@
   \centering
-  \centerline{\includegraphics[width=8.5cm]{figures/ActivationMatrix}}
+  \centerline{\includegraphics[width=6.7cm]{figures/ActivationMatrix}}
 %  \vspace{2.0cm}
@@
 
-\caption{Example of the representation of an activation matrix as a curve. \scriptsize{\textsf{\textcopyright} Own work CC BY-SA 3.0}}
+\caption{Example of the representation of an activation matrix as a curve. With a red line marking the threshold at $\frac{2}{3}$. \scriptsize{\textsf{\textcopyright} Own work CC BY-SA 3.0}}
 \label{fig:ActivationMatrix}
@@
 In order to do that the curve is first normalized.
-Afterwards a threshold of $\frac{2}{3}$ is applied.
-This value was establish empirically to separate the valid detection from false positives.
+Afterwards a threshold of $\frac{2}{3}$ is applied, which can be seen as a red line in figure \ref{fig:ActivationMatrix}.
+This value was establish empirically to separate the valid detections from false positives.
 Then the first derivative, which represents the slope of the curve, is calculated, by subtracting each element from the previous one.
 An example of the resulting curve can be found in figure \ref{fig:Ableitung}.
+In order to find the extract time points of a peak the zero crossings of the resulting curve have to be detected.
+Once the frame number of a zero crossing is found, the frame number has to be converted back to a time point.
+This is achieved by applying the following formula, where $f_s$ is the sample rate.
+
+\[
+timePoint = zeroCrossingFrameNumber * \frac{hopSize}{f_s}
+\]
+
+Due to the formula we are only able to get the time point within a range of approx. 12 ms.
+Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.
 
@@
 
-basic NMF description, our peak picking algorithm, maybe libs used
+%basic NMF description, our peak picking algorithm, maybe libs used
 
@@
 \label{sec:evaluation}
+
+As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{http://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
+The data set contains recordings of 207 drum tracks split over 3 different drum kits.
+In the data set each instrument of the drum kit is recorded separately.
+For our purposes we only uses the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
+Next to the recordings the test data set also contains a annotation file for each drum track, which lists the occurrence an instrument as well as the time point it occurred.
+This data was used as the ground truth to compare our algorithm against.
 
@@
 - adaptive threshold instead of 2/3
+- sinc interpolation to reduce epsilon
 

### 2017-08-17 Latex/Paper/main.tex
Countercheck

@@
 
-In the field of music information retrieval NMF has also been used in a variety of applications.
+In the field of MIR NMF has also been used in a variety of applications.
 Most notable are the fields of source separation and music transcription.
 For source separation the goal is to separate a piece of music containing a mix of multiple sound sources into the their components.
-T. Virtanen \cite{virtanen2007} among many others has researched this topic.
+%T. Virtanen \cite{virtanen2007} among many others has researched this topic.
+\cite{virtanen2007}
 
@@
 
-As mentioned above we used a non-negative matrix factorization to extract the time points of drum events from a drum track.
+As mentioned above we use a \textbf{non-negative matrix factorization} to extract the time points of drum events from a drum track.
 In general terms the NMF factorizes a matrix (usually called $\mathbf{V}$) into two smaller matrices (usually called $\mathbf{W}$ and $\mathbf{H}$) with the constraint that every matrix element must be non-negative.
@@
 As mentioned before a visual representations of both transformed inputs can be found in figure \ref{fig:MatrixOverview} (b) and (a) respectively.
-Before both inputs together are fed into the actual detection the drum sound undergoes some further processing.
-This step is marked as template extraction in figure \ref{fig:Flowchart}.
+
+Before both inputs are fed into the actual detection the drum sound undergoes some further processing.
+This step is marked as \textbf{template extraction} in figure \ref{fig:Flowchart}.
 %% TODO: explain transient and shit
-After both inputs are prepared they are handed over to the NMF, which does its processing in the way described in the paragraph above.
-As explained the result of the NMF is in our case the activation matrix $\mathbf{H}$.
-The matrix $\mathbf{H}$ can also be viewed as a function curve of how much the given template is contribution to the given music signal over time.
-An example of the representation of the matrix $\mathbf{H}$ as a curve can be seen in figure \ref{fig:ActivationMatrix}.
 
+After both inputs are prepared they are handed over to the NMF, which does its processing in the way described before.
+The result of the NMF is in our case the activation matrix $\mathbf{H}$.
+The matrix $\mathbf{H}$ can also be viewed as a function curve of how much the given template is contributing to the given music signal over time.
+The next step of the algorithm is called \textbf{onset detection} where we extract the exact time points from the matrix $\mathbf{H}$.
+An alternative representation of the matrix $\mathbf{H}$ as a curve can be seen in figure \ref{fig:ActivationMatrix}.
 \begin{figure}[htb]
@@
 \end{figure}
-
-The next step of the algorithm is called onset detection where the exact time points are extracted from that curve.
 The onset detection is a simple implementation loosely based on the algorithms described by Lerch \cite{lerch2012book} in chapter 6.3.
@@
 
-\[
+\begin{align}
+\label{eq:timePoint}
 timePoint = zeroCrossingFrameNumber * \frac{hopSize}{f_s}
-\]
+\end{align}
 
-Due to the formula we are only able to get the time point within a range of approx. 12 ms.
+Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms.
 Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.

### 2017-08-17 Latex/Paper/main.tex
Added abstract, finished implementation and continuted evaluation.

@@
 \begin{abstract}
-Stark verkürzte, überblicksartige Darstellung von Forschungsbedarf, Fragestellung, Methode, erwartetem
-Ergebnis und Nutzen.
-The abstract should contain about 100 to 150 words.
+Using math to do magic is easy.
+While it is very easy for us humans to find patterns and percussive events in music such a task is very difficult for a computer.
+In this research we showed that it is possible for a computer to find the exact time points of drum events in a piece of music by using non-negative matrix factorization.
+Generating such a so called drum transcription can have lots of different applications.
+By using relatively straightforward math and well established techniques that others before us have researched we hoped to get a reliable drum transcription algorithm.
+In doing so we were able to get detection rates of up to 90\%.
+
+%Stark verkürzte, überblicksartige Darstellung von Forschungsbedarf, Fragestellung, Methode, erwartetem Ergebnis und Nutzen.
+%The abstract should contain about 100 to 150 words.
 \end{abstract}
@@
 \begin{keywords}
-Non-Negative Matrix Factorization, Drum Transcription, Profit
+Drum Transcription, Non-Negative Matrix Factorization, Onset Detection%, Profit
 \end{keywords}
@@
 Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
-For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm [QUELLE].
+For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm.
 Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.
@@
 This step is marked as \textbf{template extraction} in figure \ref{fig:Flowchart}.
-%% TODO: explain transient and shit
+For our base drum template we chose to only use the transient of the base drum.
+This has the advantage that it makes the template independent of the length of the original base drum sound.
+As most of the energy is in the transient it is the most relevant part of the base drum sound.
+Using only the transient also makes the template somewhat independent of the room it was recorded in, as any possible reverberation or echo is cut off.
 
@@
 
-Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms.
+Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms (called epsilon).
 Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.
@@
 
+The implementation of our algorithm was done in Python using the numpy/scipy library stack. 
+As well as the library nimfa\footnote{\url{http://nimfa.biolab.si/}} for NMF calculations.
+The entire code repository is licensed under the GPL 3.0 and can be found on GitHub\footnote{\url{https://github.com/Bendrien/AudioContentAnalysis}}.
+
 %basic NMF description, our peak picking algorithm, maybe libs used
@@
 
-As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{http://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
+As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
 The data set contains recordings of 207 drum tracks split over 3 different drum kits.
@@
 This data was used as the ground truth to compare our algorithm against.
+
+In order to evaluate the accuracy of our algorithm we compared the drum events that our algorithm detected with the annotations of the ENST test set.
+When comparing the results we took into account the epsilon error margin of approx. 12 ms.
+
+  \begin{table}[h]
+    \centering
+    \begin{tabular}{l | c c c}
+      Drummer  &  1 & 2 & 3 \\
+      \# Files &   63 &   75 & 69 \\
+      \hline
+      Median$_{P}$   & 0.25 & 0.93 & 0.86 \\
+      Mean$_{P}$     & 0.27 & 0.89 & 0.80 \\
+      $\sigma_P$     & 0.22 & 0.12 & 0.18 \\
+      \hline
+      Median$_{FP}$   & 0.13 & 0.0 & 0.0 \\
+      Mean$_{FP}$     & 0.23 & 0.0 & 0.001 \\
+      $\sigma_{FP}$   & 0.29 & 0.0 & 0.001 \\
+    \end{tabular}
+    \caption{Results of the base drum detection. $P$ represents the true positives and $FP$ the false positives.}
+    \label{tab:results}
+  \end{table}
 

### 2017-08-17 Latex/Paper/main.tex
Finished conclusion and discussion.

@@
 
-\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
-context, problem, use cases
-definitions
-paper overview
+%\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+%context, problem, use cases
+%definitions
+%paper overview
 
@@
 
-\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
-literature review, state of the art
+%\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+%literature review, state of the art
 
@@
 
-\section{algorithm overview and description}
+\section{Algorithm overview and description}
 \label{sec:algo}
@@
 The implementation of our algorithm was done in Python using the numpy/scipy library stack. 
-As well as the library nimfa\footnote{\url{http://nimfa.biolab.si/}} for NMF calculations.
-The entire code repository is licensed under the GPL 3.0 and can be found on GitHub\footnote{\url{https://github.com/Bendrien/AudioContentAnalysis}}.
+As well as the library nimfa\footnote{NMF library: \url{http://nimfa.biolab.si/}} for NMF calculations.
+The entire code repository is licensed under the GPL 3.0 and can be found on GitHub\footnote{Repository: \url{https://github.com/Bendrien/AudioContentAnalysis}}.
 
@@
 
-As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{\url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
+As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{ENST drum test database: \url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
 The data set contains recordings of 207 drum tracks split over 3 different drum kits.
@@
 When comparing the results we took into account the epsilon error margin of approx. 12 ms.
+This leaves us with a detection rate for each track.
+To get an overall estimate of the accuracy of our algorithm we calculated the median for each drum kit as well as the mean and the standard deviation.
+Besides the true positives we also counted the false positives for each track, where our algorithm would detect a drum event, but according to the annotations there is none there.
+We calculated the median, mean and standard deviation across all tracks for the false positives as well.
+The results of our evaluation for the base drum template can be found in table \ref{tab:results}.
 
@@
   \begin{tabular}{l | c c c}
-      Drummer  &  1 & 2 & 3 \\
+      Drum kit  &  1 & 2 & 3 \\
       \# Files &   63 &   75 & 69 \\
@@
 
-ground truth, methodology, metrics
-results
-discussion
+As visible in table \ref{tab:results} the results for drum kit 2 are the best with a average of around 90\% accuracy and a fairly low standard deviation.
+The same is true for drum kit 3 which had a detection rate in the mid 80's.
+Both had none or close to no false positives.
+Drum kit 1 shows different accuracy results.
+Here only around 25\% of the base drum hits are detected correctly, while the false positive detection is also at around 20\%.
+The standard deviation is also significantly higher.
 
-- we only uses drum tracks, but it also works with mixed music. problem: ground truth
+From these results we can see that our algorithm returns very satisfying results for 2 out 3 drum kits from our test data set.
+We also found an explanation for the outlier.
+When listening to the base drum sounds of the individual drum kits it becomes obvious that drum kit 2 and 3 sound very alike with a sharp, crisp base drum sound, while the drum kit 1 sounds more smooth and mellow.
+Since the base drum template used here was extracted from the drum kit 2 it is not very surprising that the algorithm can't find it in the much different sounding drum kit 1.
+The solution to this problem would be to use a more generalized base drum template.
+This shows an apparent flaw in the design of the algorithm.
+It can only work as good as the templates it is provided with.
+If the sound the algorithm is looking for is pitched or distorted to much, it won't be picked up.
+More on how to improve this work in section \ref{sec:conclusion}.
+
+%ground truth, methodology, metrics
+%results
+%discussion
 
@@
 
-summary, noteworthy parts of the presented work,
-achievements and contributions
-possible improvements and future work
+In conclusions the algorithm returns surprising good results given its relative simplicity.
+As with all pattern matching algorithms if the feature the algorithm is looking for differs to much from the provided template the accuracy declines, even if a human listener is still able to pick them out.
+Work by Lerch et al. \cite{lerch2015} has shown that by introducing an additional step into the algorithm this problem can be mitigated.
+The step is called template adaption and happens between the NMF and the onset detection in figure \ref{fig:Flowchart}.
+Through different methods described in their paper it is possible to iteratively adapt the template to the detections in the music.
+That way an ``over-fitting'' of the template to a certain drum kit can be avoided.
 
-Improvements: 
-- Using adaptive templates like shown in \cite{lerch2015} can help the "over-fitting" of a template.
-- adaptive threshold instead of 2/3
-- sinc interpolation to reduce epsilon
+Another area of improvement is the onset detection with special focus on the peak picking algorithm.
+Here the empirically chosen threshold value of $\frac{2}{3}$ already yield good results, but it is also responsible for some missed events and some false positives.
+Using an adaptive threshold would further improve the outcome.
+
+As mentioned above he precision of the detected peak time point is is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
+The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.
+
+Originally we wanted to test our drum transcription algorithm on a piece of mixed polyphonic music instead of just drum tracks.
+Sadly we were unable to find an annotated test data set that fit our needs as a ground truth.
+Theoretically by using mixed music only the activation matrix $\mathbf{H}$ should get a bit more noisy.
+Everything else should work as described here.
+
+In closing we have presented an algorithm in this paper that gives satisfying results when trying to extract the exact time points at which base drum hits happen in a drum track.
+It can easily be extended to other percussive instruments and maybe even other melodic instruments.
+The accuracy and precision could be improved in future work by the methods mentioned.
+
+%summary, noteworthy parts of the presented work,
+%achievements and contributions
+%possible improvements and future work
 

### 2017-08-17 Latex/Paper/main.tex
Removed a bunch of useless shit.

@@
 
-\vfill\pagebreak
-~
-\vfill\pagebreak
-
-The abstract should appear at the top of the left-hand column of text, about
-0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
-length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
-beginning of the main text.  The abstract should contain about 100 to 150
-words, and should be identical to the abstract text submitted electronically
-along with the paper cover sheet.  All manuscripts must be in English, printed
-in black ink.
-
-These guidelines include complete descriptions of the fonts, spacing, and
-related information for producing your proceedings manuscripts. Please follow
-them and if you have any questions, direct them to Conference Management
-Services, Inc.: Phone +1-979-846-6800 or email
-to \\\texttt{papers@icassp2016.org}.
-
-\section{Formatting your paper}
-\label{sec:format}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
-not write or print anything outside the print area. The top margin must be 1
-inch (25 mm), except for the title page, and the left margin must be 0.75 inch
-(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
-inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
-fully justified.
-
-\section{PAGE TITLE SECTION}
-\label{sec:pagestyle}
-
-The paper title (on the first page) should begin 1.38 inches (35 mm) from the
-top edge of the page, centered, completely capitalized, and in Times 14-point,
-boldface type.  The authors' name(s) and affiliation(s) appear below the title
-in capital and lower case letters.  Papers with multiple authors and
-affiliations may require two or more lines for this information. Please note
-that papers should not be submitted blind; include the authors' names on the
-PDF.
-
-\section{TYPE-STYLE AND FONTS}
-\label{sec:typestyle}
-
-To achieve the best rendering both in printed proceedings and electronic proceedings, we
-strongly encourage you to use Times-Roman font.  In addition, this will give
-the proceedings a more uniform look.  Use a font that is no smaller than nine
-point type throughout the paper, including figure captions.
-
-In nine point type font, capital letters are 2 mm high.  {\bf If you use the
-smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
-vertically.}  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
-the paper much more readable.  Larger type sizes require correspondingly larger
-vertical spacing.  Please do not double-space your paper.  TrueType or
-Postscript Type 1 fonts are preferred.
-
-The first paragraph in each section should not be indented, but all the
-following paragraphs within the section should be indented as these paragraphs
-demonstrate.
-
-\section{MAJOR HEADINGS}
-\label{sec:majhead}
-
-Major headings, for example, "1. Introduction", should appear in all capital
-letters, bold face if possible, centered in the column, with one blank line
-before, and one blank line after. Use a period (".") after the heading number,
-not a colon.
-
-\subsection{Subheadings}
-\label{ssec:subhead}
-
-Subheadings should appear in lower case (initial word capitalized) in
-boldface.  They should start at the left margin on a separate line.
-
-\subsubsection{Sub-subheadings}
-\label{sssec:subsubhead}
-
-Sub-subheadings, as in this paragraph, are discouraged. However, if you
-must use them, they should appear in lower case (initial word
-capitalized) and start at the left margin on a separate line, with paragraph
-text beginning on the following line.  They should be in italics.
-
-\section{PRINTING YOUR PAPER}
-\label{sec:print}
-
-Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
-paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
-empty at the BOTTOM of the page and follow the top and left margins as
-specified.  If the last page of your paper is only partially filled, arrange
-the columns so that they are evenly balanced if possible, rather than having
-one long column.
-
-In LaTeX, to start a new column (but not a new page) and help balance the
-last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
-demonstrated on this page (see the LaTeX source below).
-
-\section{PAGE NUMBERING}
-\label{sec:page}
-
-Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
-conference identification will be inserted when the paper is included in the
-proceedings.
-
-\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
-\label{sec:illust}
-
-Illustrations must appear within the designated margins.  They may span the two
-columns.  If possible, position illustrations at the top of columns, rather
-than in the middle or at the bottom.  Caption and number every illustration.
-All halftone illustrations must be clear black and white prints.  Colors may be
-used, but they should be selected so as to be readable when printed on a
-black-only printer.
-
-Since there are many ways, often incompatible, of including images (e.g., with
-experimental results) in a LaTeX document, below is an example of how to do
-this.
-
-\section{FOOTNOTES}
-\label{sec:foot}
-
-Use footnotes sparingly (or not at all!) and place them at the bottom of the
-column on the page on which they are referenced. Use Times 9-point type,
-single-spaced. To help your readers, avoid using footnotes altogether and
-include necessary peripheral observations in the text (within parentheses, if
-you prefer, as in this sentence).
-
-% Below is an example of how to insert images. Delete the ``\vspace'' line,
-% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
-% with a suitable PostScript file name.
-% -------------------------------------------------------------------------
-\begin{figure}[htb]
-
-\begin{minipage}[b]{1.0\linewidth}
-  \centering
-  \centerline{\includegraphics[width=8.5cm]{figures/image1}}
-%  \vspace{2.0cm}
-  \centerline{(a) Result 1}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{figures/image3}}
-%  \vspace{1.5cm}
-  \centerline{(b) Results 3}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{figures/image4}}
-%  \vspace{1.5cm}
-  \centerline{(c) Result 4}\medskip
-\end{minipage}
-%
-\caption{Example of placing a figure with experimental results.}
-\label{fig:res}
-%
-\end{figure}
-
-% To start a new column (but not a new page) and help balance the last-page
-% column length use \vfill\pagebreak.
-% -------------------------------------------------------------------------
-%\vfill
-%\pagebreak
-
-\section{COPYRIGHT FORMS}
-\label{sec:copyright}
-
-You must submit your fully completed, signed IEEE electronic copyright release
-form when you submit your paper. We {\bf must} have this form before your paper
-can be published in the proceedings.
-
-\section{RELATION TO PRIOR WORK}
-\label{sec:prior}
-
-The text of the paper should contain discussions on how the paper's
-contributions are related to prior work in the field. It is important
-to put new work in  context, to give credit to foundational work, and
-to provide details associated with the previous work that have appeared
-in the literature. This discussion may be a separate, numbered section
-or it may appear elsewhere in the body of the manuscript, but it must
-be present.
-
-You should differentiate what is new and how your work expands on
-or takes a different path from the prior studies. An example might
-read something to the effect: "The work presented here has focused
-on the formulation of the ABC algorithm, which takes advantage of
-non-uniform time-frequency domain analysis of data. The work by
-Smith and Cohen considers only fixed time-domain analysis and
-the work by Jones et al takes a different approach based on
-fixed frequency partitioning. While the present study is related
-to recent approaches in time-frequency analysis [3-5], it capitalizes
-on a new feature space, which was not considered in these earlier
-studies."
-
-\vfill\pagebreak
-
-\section{REFERENCES}
-\label{sec:refs}
-
-List and number all bibliographical references at the end of the
-paper. The references can be numbered in alphabetic order or in
-order of appearance in the document. When referring to them in
-the text, type the corresponding reference number in square
-brackets as shown at the end of this sentence. An
-additional final page (the fifth page, in most cases) is
-allowed, but must contain only references to the prior
-literature.
-
 \end{document}

### 2017-08-17 Latex/Paper/main.tex
Bad results :(

@@
 In the data set each instrument of the drum kit is recorded separately.
-For our purposes we only uses the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
-Next to the recordings the test data set also contains a annotation file for each drum track, which lists the occurrence an instrument as well as the time point it occurred.
+For our purposes we use the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
+Next to the recordings the test data set also contains an annotation file for each drum track, which lists the occurrence of an instrument as well as the time point it occurred.
 This data was used as the ground truth to compare our algorithm against.
@@
   \end{tabular}
-  \caption{Results of the base drum detection. $P$ represents the true positives and $FP$ the false positives.}
+  \caption{Results of the base drum detection. $_P$ represents the true positives and $_{FP}$ the false positives.}
   \label{tab:results}

### 2017-08-17 Projekt/main.py

@@ -13,8 +13,13 @@ from os import path
 
 def main():
 
-    # load the bass drum template
-    fs, bdTemplate = getNormalizedAudio("base_drum.wav")
+    # load the drum templates
+    fs, sdTemplate = getNormalizedAudio("001_hits_snare-drum_sticks.wav")
+    fs, bdTemplate = getNormalizedAudio("004_hits_bass-drum_pedal.wav")
+    fs, ohhTemplate = getNormalizedAudio("005_hits_open-hi-hat_sticks.wav")
+    fs, chhTemplate = getNormalizedAudio("006_closed-hi-hat_sticks.wav")
+    fs, rc3Template = getNormalizedAudio("008_hits_ride-cymbal-1_sticks.wav")
+    fs, cbTemplate = getNormalizedAudio("013_hits_cowbell_sticks.wav")
 
     # plt.plot(template)
     # plt.axvspan(0, 1024, color='red', alpha=0.5)
@@ -23,7 +28,13 @@ def main():
     # plt.savefig("BassdrumTemplate.pdf")
     # plt.show()
 
-    data = [[2, "bd", bdTemplate], [2, "chh", bdTemplate]]
+    # Prepare the data
+    # data = [[2, "sd", sdTemplate]]
+    # data = [[2, "bd", bdTemplate]]
+    # data = [[2, "ohh", ohhTemplate]]
+    data = [[2, "chh", chhTemplate]]
+    # data = [[2, "rc3", rc3Template]]
+    # data = [[2, "cb", cbTemplate]]
     for drummer, drumName, template in data:
 
         # setup the file directories
@@ -61,8 +72,8 @@ def main():
 
             # write results
             resultFilename = "../../Results/Drummer_" + str(drummer) + "/" + filename + "_" + drumName + ".txt"
-            # print("Writing individual results to \"" + filename + "\"")
             file = open(resultFilename, "w")
+            file.write("[result, ground truth time, estimated time, difference]\n\n")
             file.write(str(result))
             file.close()
 
@@ -73,7 +84,7 @@ def main():
 
             # count analyzed tracks
             numberOfAnalyzedTracks += 1
-            if numberOfAnalyzedTracks > 1: break
+            #if numberOfAnalyzedTracks > 1: break
 
         writeResults(drummer, drumName, numberOfAnalyzedTracks, positives, false_positives, trackNames)
         print("\n")
[…]

### 2017-08-17 Latex/Paper/main.tex
Countercheck

@@
 
-As mentioned above he precision of the detected peak time point is is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
+As mentioned above he precision of the detected peak time point is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
 The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.
@@
 
-In closing we have presented an algorithm in this paper that gives satisfying results when trying to extract the exact time points at which base drum hits happen in a drum track.
+In closing we have presented an algorithm in this paper that gives satisfying results when trying to exact the exact time points at which base drum hits happen in a drum track.
 It can easily be extended to other percussive instruments and maybe even other melodic instruments.

### 2017-08-17 Latex/Paper/main.tex
Last corrections and python changes for the plots.

--- 2017-08-17 Latex/Paper/main.tex
@@
 Using math to do magic is easy.
-While it is very easy for us humans to find patterns and percussive events in music such a task is very difficult for a computer.
-In this research we showed that it is possible for a computer to find the exact time points of drum events in a piece of music by using non-negative matrix factorization.
-Generating such a so called drum transcription can have lots of different applications.
+While it is very easy for us humans to find patterns and percussive events in music such a task is very difficult to a computer.
+In this research we show that it is possible for a computer to find the exact time points of drum events in a piece of music by using non-negative matrix factorization.
+Generating such a so called drum transcription is useful in lots of different applications.
 By using relatively straightforward math and well established techniques that others before us have researched we hoped to get a reliable drum transcription algorithm.
@@
 This list of time points and a corresponding flag with the kind of the drum event is called the drum transcription. 
-While in theory this can be used to find any kind of event within a musical piece, we focused mainly on basic drum sounds in our research.
+While in theory the proposed algorithm can be used to find any kind of event within a musical piece, we focused mainly on basic drum sounds in our research.
 
-The transcription of the drum track of a song can be useful in many cases.
+The transcription of a songs drum track can be useful in many cases.
 The simplest would be to generate the sheet music for a song where the original has been lost or is not available.
@@
 Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
-For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm.
+For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection or song segmentation algorithm.
 Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.
@@
 
-The idea to use NMF for pattern recognition was first proposed by Lee and Seung in 1999 \cite{lee1999}.
+The idea to use NMF for pattern recognition was first proposed in a paper by Lee and Seung in 1999 \cite{lee1999}.
 As described in their paper NMF is a versatile technique to find features in a data set.
@@
 
-In the field of MIR NMF has also been used in a variety of applications.
+In the field of MIR NMF has also been used in a variety of different applications.
 Most notable are the fields of source separation and music transcription.
 For source separation the goal is to separate a piece of music containing a mix of multiple sound sources into the their components.
-%T. Virtanen \cite{virtanen2007} among many others has researched this topic.
-\cite{virtanen2007}
+T. Virtanen \cite{virtanen2007} among many others has researched this topic. % ich würde den satz drinn lassen, weil Virtanen ein Guru auf dem NMF gebiet ist. Name dropping und so!
+%\cite{virtanen2007}
 
@@
 
-As mentioned above we use a \textbf{non-negative matrix factorization} to extract the time points of drum events from a drum track.
+As mentioned above we used a \textbf{non-negative matrix factorization} to extract the time points of drum events from a drum track.
 In general terms the NMF factorizes a matrix (usually called $\mathbf{V}$) into two smaller matrices (usually called $\mathbf{W}$ and $\mathbf{H}$) with the constraint that every matrix element must be non-negative.
@@
 
-In our case we use the magnitude spectrum of a song as the $\mathbf{V}$ matrix and decomposed it into two matrices.
-The first one contains the magnitude spectra of the individual components we are interested in ($\mathbf{W}$) and the second one contains the time-varying gain of these components ($\mathbf{H}$), which tells us when each of the components for the first matrix is active.
+In our case we used the magnitude spectrum of a song as the $\mathbf{V}$ matrix and decompose it into two matrices.
+The first one contains the magnitude spectra of the individual components we are interested in ($\mathbf{W}$) and the second one contains the time-varying gain of these components ($\mathbf{H}$), which tells us when each of the components form the first matrix is active.
 For that reason the $\mathbf{W}$ matrix is usually called component matrix and $\mathbf{H}$ is usually called activation matrix.
@@
 A visual representation of that can be seen in figure \ref{fig:MatrixOverview} (d).
+The constraint of only using non-negative numbers is met since we are using magnitude spectra which by definition only contain non-negative number.
 
@@
 In order to do so, we specified $\mathbf{W}$ as the spectrum of a base drum (see figure \ref{fig:MatrixOverview} (b)) and $\mathbf{V}$ continued to be the spectrum of the whole song (see figure \ref{fig:MatrixOverview} (a)).
-The NMF then solves for the matrix $\mathbf{H}$ (see figure \ref{fig:MatrixOverview} (c)) which tells us at what point in time the specified base drum spectrum appears in the song.
-In that setup the NMF essentially works as a pattern matching algorithm.
+The NMF then solved for the matrix $\mathbf{H}$ (see figure \ref{fig:MatrixOverview} (c)) which told us at what point in time the specified base drum spectrum appears in the song.
+In that setup the NMF essentially worked as a pattern matching algorithm.
 
@@
 On the left hand side the two inputs to the algorithms are shown.
-The first input is a time domain signal of percussive instrument, like a base drum or hi-hat, and the second input is a time domain signal of a piece of music.
+The first input is a time domain signal of a percussive instrument, like a base drum or hi-hat, and the second input is a time domain signal of a piece of music.
 For both inputs the first step is to down mix the signals into a mono signal.
@@
 We also chose an overlap of 50\% between hops to improve the time resolution.
+A Hann window was applied to reduce spectral leakage.
 As mentioned before a visual representations of both transformed inputs can be found in figure \ref{fig:MatrixOverview} (b) and (a) respectively.
@@
 
-After both inputs are prepared they are handed over to the NMF, which does its processing in the way described before.
-The result of the NMF is in our case the activation matrix $\mathbf{H}$.
+After both inputs are prepared they were handed over to the NMF, which does its processing in the way described above.
+The result of the NMF was in our case the activation matrix $\mathbf{H}$.
 The matrix $\mathbf{H}$ can also be viewed as a function curve of how much the given template is contributing to the given music signal over time.
-The next step of the algorithm is called \textbf{onset detection} where we extract the exact time points from the matrix $\mathbf{H}$.
+The next step of the algorithm is called \textbf{onset detection} where we extracted the exact time points from the matrix $\mathbf{H}$.
 An alternative representation of the matrix $\mathbf{H}$ as a curve can be seen in figure \ref{fig:ActivationMatrix}.
@@
 To extract the onsets of the drum events the significant local maxima of the curve (peaks) have to be detected.
-In order to do that the curve is first normalized.
-Afterwards a threshold of $\frac{2}{3}$ is applied, which can be seen as a red line in figure \ref{fig:ActivationMatrix}.
+In order to do that the curve was first normalized.
+Afterwards a threshold of $\frac{2}{3}$ was applied, which can be seen as a red line in figure \ref{fig:ActivationMatrix}.
 This value was establish empirically to separate the valid detections from false positives.
-Then the first derivative, which represents the slope of the curve, is calculated, by subtracting each element from the previous one.
+Then the first derivative, which represents the slope of the curve, was calculated, by subtracting each element from the previous one.
 An example of the resulting curve can be found in figure \ref{fig:Ableitung}.
-In order to find the extract time points of a peak the zero crossings of the resulting curve have to be detected.
-Once the frame number of a zero crossing is found, the frame number has to be converted back to a time point.
-This is achieved by applying the following formula, where $f_s$ is the sample rate.
+In order to find the extract time points of a peak the zero crossings of the resulting curve had to be detected.
+Once the frame number of a zero crossing was found, the frame number had to be converted back to a time point.
+This was achieved by applying the following formula, where $f_s$ is the sample rate.
 
@@
 
-Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms (called epsilon).
-Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.
+Due to the formula \ref{eq:timePoint} we were only able to get the time point within a range of approx. 12 ms (called epsilon).
+Once this calculation was done we received a list of time points where the given template was found in the song which is the drum transcription we were looking for.
 
@@
 
-As our test data set we used the ENST-drums database of the Institut Télécom Paris Tech\footnote{ENST drum test database: \url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
+As our test data set we used the ENST-drums database kindly provided by the Institut Télécom Paris Tech\footnote{ENST drum test database: \url{https://perso.telecom-paristech.fr/~grichard/ENST-drums/}}.
 The data set contains recordings of 207 drum tracks split over 3 different drum kits.
 In the data set each instrument of the drum kit is recorded separately.
-For our purposes we use the mixed version of the tracks called ``wet-mix'' which also contains some acoustic elements of the recording room, like reverberation, making it more realistic for real world applications.
+For our purposes we use the mixed version of the tracks called ``wet-mix'' which also contains some acoustic room elements, like reverberation, making it more suitable as a test data set for real world applications.
 Next to the recordings the test data set also contains an annotation file for each drum track, which lists the occurrence of an instrument as well as the time point it occurred.
@@
 When comparing the results we took into account the epsilon error margin of approx. 12 ms.
-This leaves us with a detection rate for each track.
+This left us with a detection rate for each track.
 To get an overall estimate of the accuracy of our algorithm we calculated the median for each drum kit as well as the mean and the standard deviation.
@@
 
-From these results we can see that our algorithm returns very satisfying results for 2 out 3 drum kits from our test data set.
+From these results we can see that our algorithm returns very satisfying results for 2 out of 3 drum kits from our test data set.
 We also found an explanation for the outlier.
@@
 This shows an apparent flaw in the design of the algorithm.
-It can only work as good as the templates it is provided with.
+It can only work as well as the templates it is provided with.
 If the sound the algorithm is looking for is pitched or distorted to much, it won't be picked up.
@@
 Another area of improvement is the onset detection with special focus on the peak picking algorithm.
-Here the empirically chosen threshold value of $\frac{2}{3}$ already yield good results, but it is also responsible for some missed events and some false positives.
-Using an adaptive threshold would further improve the outcome.
+Here the empirically chosen threshold value of $\frac{2}{3}$ already yields good results, but it is also responsible for some missed events and some false positives.
+Using an adaptive threshold would further improve the results.
 
-As mentioned above he precision of the detected peak time point is is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
+As mentioned above the precision of the detected peak time point is only precise within a range of approx. 12 ms since only the STFT frame in which the peak occurs can be tracked.
 The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.

### 2017-08-17 Projekt/main.py

@@ -30,9 +30,9 @@ def main():
 
     # Prepare the data
     # data = [[2, "sd", sdTemplate]]
-    # data = [[2, "bd", bdTemplate]]
+    data = [[2, "bd", bdTemplate]]
     # data = [[2, "ohh", ohhTemplate]]
-    data = [[2, "chh", chhTemplate]]
+    # data = [[2, "chh", chhTemplate]]
     # data = [[2, "rc3", rc3Template]]
     # data = [[2, "cb", cbTemplate]]
     for drummer, drumName, template in data:
@@ -42,7 +42,10 @@ def main():
         annotationPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/annotation/"
 
         # get all audio file names
-        allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
+        #allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
+
+        # TO BE REMOVED: test track for the plots
+        allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
 
         print("Transcripting: " + drumName + " of drummer " + str(drummer) + "\n=============")
 
@@ -203,6 +206,7 @@ def findTemplate(audio, template, annotations, fs):
 
     # plt.figure()
     # plt.plot(Harray)
+    # plt.xlabel("STFT frame number")
     # plt.savefig("ZeroCrosses.pdf", bbox_inches='tight')
     # plt.show()
 

### 2017-08-18 Projekt/main.py
Rewrite compare_time fucntion

@@ -35,6 +35,8 @@ def main():
     # data = [[2, "chh", chhTemplate]]
     # data = [[2, "rc3", rc3Template]]
     # data = [[2, "cb", cbTemplate]]
+    data = [[1, "bd", bdTemplate], [2, "bd", bdTemplate], [3, "bd", bdTemplate]]
+
     for drummer, drumName, template in data:
 
         # setup the file directories
@@ -42,10 +44,10 @@ def main():
         annotationPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/annotation/"
 
         # get all audio file names
-        #allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
+        allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
 
         # TO BE REMOVED: test track for the plots
-        allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
+        #allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
 
         print("Transcripting: " + drumName + " of drummer " + str(drummer) + "\n=============")
 
@@ -73,33 +75,50 @@ def main():
             # find the drum sound
             result = findTemplate(audio, template, annotations, fs)
 
-            # write results
-            resultFilename = "../../Results/Drummer_" + str(drummer) + "/" + filename + "_" + drumName + ".txt"
-            file = open(resultFilename, "w")
-            file.write("[result, ground truth time, estimated time, difference]\n\n")
-            file.write(str(result))
-            file.close()
-
             # remember statistics
-            positives.append(count_positives(result) / annotations[:, 0].size)
-            false_positives.append((count_false_positives(result) + count_overflow(result)) / result[:, 0].size)
+            positives_count = count_positives(result)
+            false_positives_count = count_false_positives(result) + count_overflow(result)
+            annotation_count = annotations[:, 0].size
+            result_count = result[:, 0].size
+            writeTrackResults(drummer, filename, drumName, annotation_count,
+                              positives_count, false_positives_count, result)
+
+            positives.append(positives_count / annotation_count)
+            false_positives.append(false_positives_count / result_count)
             trackNames.append(filename)
 
             # count analyzed tracks
             numberOfAnalyzedTracks += 1
-            #if numberOfAnalyzedTracks > 1: break
+            #if numberOfAnalyzedTracks >= 2: break
 
[…]

### 2017-08-18 Projekt/main.py
Add x and y labels to figures

@@ -35,7 +35,8 @@ def main():
     # data = [[2, "chh", chhTemplate]]
     # data = [[2, "rc3", rc3Template]]
     # data = [[2, "cb", cbTemplate]]
-    data = [[1, "bd", bdTemplate], [2, "bd", bdTemplate], [3, "bd", bdTemplate]]
+    #data = [[1, "bd", bdTemplate], [2, "bd", bdTemplate], [3, "bd", bdTemplate]]
+    #data = [[1, "chh", chhTemplate], [2, "chh", chhTemplate], [3, "chh", chhTemplate]]
 
     for drummer, drumName, template in data:
 
@@ -47,7 +48,7 @@ def main():
         allAudioFiles = [f for f in listdir(audioPath) if path.isfile(path.join(audioPath, f)) and f.endswith(".wav")]
 
         # TO BE REMOVED: test track for the plots
-        #allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
+        allAudioFiles = ["045_phrase_rock_simple_medium_sticks.wav"]
 
         print("Transcripting: " + drumName + " of drummer " + str(drummer) + "\n=============")
 
@@ -73,7 +74,7 @@ def main():
             fs, audio = getNormalizedAudio(audioPath + audioFile)
 
             # find the drum sound
-            result = findTemplate(audio, template, annotations, fs)
+            result = findTemplate(audio, template, annotations, fs, drumName)
 
             # remember statistics
             positives_count = count_positives(result)
@@ -95,87 +96,59 @@ def main():
         print("\n")
 
 
-def writeTrackResults(drummer, filename, drumName, annotation_count, positives_count, false_positives_count, result):
-    resultFilename = "../../Results/Drummer_" + str(drummer) + "/" + filename + "_" + drumName + ".txt"
-    file = open(resultFilename, "w")
-    file.write("# Track Results")
-    file.write("\nThere are " + str(result[:, 0].size) + " result entries compared to " + str(annotation_count)
-               + " annotations in track \"" + filename + "\".")
-    file.write("\nPositives:\t" + str(positives_count))
-    file.write("\nFalse positives:\t" + str(false_positives_count))
 
-    file.write("\n\n## Result legend")
-    file.write("\nResult mapping:\tUNDERFLOW (-2), LOWER (-1), EQUAL (0), UPPER (1), OVERFLOW (2)")
[…]

### 2017-08-18 Latex/Paper/main.tex
Overall corrections

--- 2017-08-17 Latex/Paper/main.tex
@@
   \centering
-  \centerline{\includegraphics[width=6.7cm]{figures/ActivationMatrix}}
+  \centerline{\includegraphics[width=8.5cm]{figures/ActivationMatrix}}
 %  \vspace{2.0cm}
@@
 
-\begin{align}
+\begin{align*}
 \label{eq:timePoint}
 timePoint = zeroCrossingFrameNumber * \frac{hopSize}{f_s}
-\end{align}
+\end{align*}
 
-Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms (called epsilon).
+Due to this formula we are only able to get the time point within a range of approx. 12 ms (called epsilon).
 Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.
@@
 
-As mentioned above he precision of the detected peak time point is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
-The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.
+As mentioned above the precision of the detected peak time point is only precise within an epsilon range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
+By interpolating between nearby frames the accuracy of the point of inflection could be improved making the epsilon range significant smaller.
 

### 2017-08-18 Latex/Paper/main.tex
final work through the paper

@@
 \begin{abstract}
-Using math to do magic is easy.
-While it is very easy for us humans to find patterns and percussive events in music such a task is very difficult for a computer.
-In this research we showed that it is possible for a computer to find the exact time points of drum events in a piece of music by using non-negative matrix factorization.
-Generating such a so called drum transcription can have lots of different applications.
-By using relatively straightforward math and well established techniques that others before us have researched we hoped to get a reliable drum transcription algorithm.
-In doing so we were able to get detection rates of up to 90\%.
+% Using math to do magic is easy. % lol wat?
+While humans are naturally capable of detecting patterns like percussive events in music such a task is difficult for a computer.
+In this research we analyze the possibilities of finding the time points of drum events in a piece of music by using non-negative matrix factorization.
+Generating a so called drum transcription can have lots of different applications.
+By using well established techniques based on preceding research we hope to get a reliable drum transcription algorithm with detection rates of up to 90\%.
 
@@
 \begin{keywords}
-Drum Transcription, Non-Negative Matrix Factorization, Onset Detection%, Profit
+Drum Transcription, Non-Negative Matrix Factorization, Onset Detection, Music Information Retrieval
 \end{keywords}
@@
 
-For this research paper we looked into the topic of generating a drum transcription from a piece of music containing a recording of a drum kit.
+For this research we look into the topic of generating a transcription of drums from a piece of music containing a recording of a drum kit.
 Drum transcription is considered a classical music information retrieval (MIR) problem, where you want to extract information from a mixed piece of music.
@@
 This list of time points and a corresponding flag with the kind of the drum event is called the drum transcription. 
-While in theory this can be used to find any kind of event within a musical piece, we focused mainly on basic drum sounds in our research.
+While in theory this can be used to find any kind of event within a musical piece, we focus mainly on basic drum sounds in our research.
 
@@
 Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
-For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm.
+For example using the results of the drum transcription a Beats per Minute detection can be build, which in turn can then be the basis of a tempo detection algorithm.
 Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.
@@
 On first sight extracting the time point of a drum hit for a polyphonic, mixed piece of music sounds like a difficult task.
-In fact though there are multiple mathematically simple algorithm to achieve that.
-For this research we took an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).
-Section \ref{sec:algo} will show a detailed explanation of how the NMF works.
+In fact though there are multiple algorithms to achieve that.
+For this research we take an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).
+
+After introducing the current state in research of this subject area in section \ref{sec:rel} we give a detailed explanation of how the NMF and our algorithm works in section \ref{sec:algo}.
+In section \ref{sec:evaluation} we evaluate our results and come to a conclusion in section \ref{sec:conclusion}.
 
@@
 
-The idea to use NMF for pattern recognition was first proposed by Lee and Seung in 1999 \cite{lee1999}.
+The idea to use NMF for pattern recognition was first proposed by Lee and Seung in 1999. \cite{lee1999}
 As described in their paper NMF is a versatile technique to find features in a data set.
@@
 
-In the field of music transcription NMF has also been used for different topics.
+In the field of music transcription NMF has also been used for several topics.
 Smaragdis and Brown \cite{smaragdis2003} used NMF to analyze and extract polyphonic, harmonic content from a piece of music.
@@
 Again the sum of both of these matrices makes up an approximation of the original spectrum \cite{smaragdis2003}.
-A visual representation of that can be seen in figure \ref{fig:MatrixOverview} (d).
+A visual representation of all these matrices can be seen in figure \ref{fig:MatrixOverview}.
 
-For our use case we were not interested in finding all the components and their activations.
-We were rather interested in finding the corresponding activation of a specific component, like that of a base drum or a hi-hat.
+For our use case we are not interested in finding all the components and their activations.
+We are rather interested in finding the corresponding activation of a specific component, like that of a base drum or a hi-hat.
 This is also possible using NMF.
-In order to do so, we specified $\mathbf{W}$ as the spectrum of a base drum (see figure \ref{fig:MatrixOverview} (b)) and $\mathbf{V}$ continued to be the spectrum of the whole song (see figure \ref{fig:MatrixOverview} (a)).
-The NMF then solves for the matrix $\mathbf{H}$ (see figure \ref{fig:MatrixOverview} (c)) which tells us at what point in time the specified base drum spectrum appears in the song.
+In order to do so, we specify $\mathbf{W}$ as the spectrum of a base drum (see figure \ref{fig:MatrixOverview} (b)) and $\mathbf{V}$ continues to be the spectrum of the whole song (see figure \ref{fig:MatrixOverview} (a)).
+The NMF then solves for the matrix $\mathbf{H}$ (see figure \ref{fig:MatrixOverview} (c)) which tells us at what frame the specified base drum spectrum appears in the song.
 In that setup the NMF essentially works as a pattern matching algorithm.
@@
 On the left hand side the two inputs to the algorithms are shown.
-The first input is a time domain signal of percussive instrument, like a base drum or hi-hat, and the second input is a time domain signal of a piece of music.
+The first input is a time domain signal of percussive instrument, like a base drum, and the second input is a time domain signal of a piece of music.
 For both inputs the first step is to down mix the signals into a mono signal.
-Next the short-time Fourier transform (STFT) is applied, which transforms both signal from the time domain to the frequency domain.
-For the parameters of the STFT we used a frame size of 1024 samples which yields in a frequency resolution of approx. 43 Hz per bin.
+Next the short-time Fourier transform (STFT) is applied, which transforms both signals from the time domain to the frequency domain.
+For the parameters of the STFT we use a frame size of 1024 samples which yields in a frequency resolution of approx. 43 Hz per bin.
 We also chose an overlap of 50\% between hops to improve the time resolution.
-As mentioned before a visual representations of both transformed inputs can be found in figure \ref{fig:MatrixOverview} (b) and (a) respectively.
+A visual representations of both transformed inputs can be seen in figure \ref{fig:MatrixOverview} (a) and (b) respectively.
 
@@
 The matrix $\mathbf{H}$ can also be viewed as a function curve of how much the given template is contributing to the given music signal over time.
-The next step of the algorithm is called \textbf{onset detection} where we extract the exact time points from the matrix $\mathbf{H}$.
+The next step of the algorithm is called \textbf{onset detection} where we extract the time points for an percussive event from the matrix $\mathbf{H}$.
 An alternative representation of the matrix $\mathbf{H}$ as a curve can be seen in figure \ref{fig:ActivationMatrix}.
@@
 
-The implementation of our algorithm was done in Python using the numpy/scipy library stack. 
+The implementation of our algorithm is done in Python using the numpy/scipy library stack. 
 As well as the library nimfa\footnote{NMF library: \url{http://nimfa.biolab.si/}} for NMF calculations.
@@
       \hline
-      Median$_{FP}$   & 0.13 & 0.0 & 0.0 \\
-      Mean$_{FP}$     & 0.23 & 0.0 & 0.001 \\
-      $\sigma_{FP}$   & 0.29 & 0.0 & 0.001 \\
+      Median$_{FP}$   & 0.21 & 0.0 & 0.05 \\
+      Mean$_{FP}$     & 0.34 & 0.02 & 0.07 \\
+      $\sigma_{FP}$   & 0.31 & 0.04 & 0.07 \\
   \end{tabular}
@@
 Drum kit 1 shows different accuracy results.
-Here only around 25\% of the base drum hits are detected correctly, while the false positive detection is also at around 20\%.
+Here only around 25\% of the base drum hits are detected correctly, while the false positive detection is also at around 21\%.
 The standard deviation is also significantly higher.
@@
 
-In conclusions the algorithm returns surprising good results given its relative simplicity.
+The algorithm returns good results given its relative simplicity.
 As with all pattern matching algorithms if the feature the algorithm is looking for differs to much from the provided template the accuracy declines, even if a human listener is still able to pick them out.

### 2017-08-18 Latex/Paper/main.tex
Final final

@@
 
-In closing we have presented an algorithm in this paper that gives satisfying results when trying to exact the exact time points at which base drum hits happen in a drum track.
+In closing we have presented an algorithm that gives satisfying results when trying to exact the time points at which base drum hits happen in a drum track.
 It can easily be extended to other percussive instruments and maybe even other melodic instruments.
@@
 
-%\end{document}
-
-% DELETE EVERYTHING FROM HERE IN THE END
-% DELETE EVERYTHING FROM HERE IN THE END
-% DELETE EVERYTHING FROM HERE IN THE END
-
-\vfill\pagebreak
-
-\section{common flaws}
-all cited papers should appear in bibliography
-vice versa: all references should be mentioned in the paper
-each reference should contain:
-names of authors
-title of the paper or book
-conference paper: name of conf. incl. year and location
-journal paper: name of journal incl. volume, year and pages
-book: publisher, potentially editor
-all figures and tables must be referenced in the paper
-equations:
-all mathematical symbols must be explained
-symbols should be used consistently and unambiguously
-abbreviations (STFT, DFT, etc.) should be introduced
-”The short-time Fourier transform (STFT) is given by (. . .)
-We compute the STFT of the signal, (. . .)”
-
-\section{Evaluation}
-
-form (structure, language, form of references)
-content (introduction, literature review, algorithm and
-evaluation description, figures, comprehensibility, correctness)
-evaluation (dataset, metrics, discussion)
-
 \end{document}

### 2017-08-18 Projekt/transcript.py

@@ -1,8 +1,5 @@
 import pydub as pd
 import numpy as np
-import itertools
-import matplotlib.pyplot as plt
-from matplotlib.colors import LogNorm
 import math
 import csv
 import nimfa
@@ -12,43 +9,23 @@ from os import path
 
 
 def main():
+    print("\n\t> NOTE: please follow the instructions of the Readme.md <\n")
 
-    # load the drum templates
-    fs, sdTemplate = getNormalizedAudio("001_hits_snare-drum_sticks.wav")
+    # load the drum template
     fs, bdTemplate = getNormalizedAudio("004_hits_bass-drum_pedal.wav")
-    fs, ohhTemplate = getNormalizedAudio("005_hits_open-hi-hat_sticks.wav")
-    fs, chhTemplate = getNormalizedAudio("006_closed-hi-hat_sticks.wav")
-    fs, rc3Template = getNormalizedAudio("008_hits_ride-cymbal-1_sticks.wav")
-    fs, cbTemplate = getNormalizedAudio("013_hits_cowbell_sticks.wav")
-
-    # plt.plot(template)
-    # plt.axvspan(0, 1024, color='red', alpha=0.5)
-    # plt.xlabel("Sample")
-    # plt.ylabel("Amplitude")
-    # plt.savefig("BassdrumTemplate.pdf")
-    # plt.show()
 
     # Prepare the data
-    # data = [[2, "sd", sdTemplate]]
-    data = [[2, "bd", bdTemplate]]
-    # data = [[2, "ohh", ohhTemplate]]
-    # data = [[2, "chh", chhTemplate]]
-    # data = [[2, "rc3", rc3Template]]
-    # data = [[2, "cb", cbTemplate]]
-    #data = [[1, "bd", bdTemplate], [2, "bd", bdTemplate], [3, "bd", bdTemplate]]
-    #data = [[1, "chh", chhTemplate], [2, "chh", chhTemplate], [3, "chh", chhTemplate]]
+    data = [[1, "bd", bdTemplate], [2, "bd", bdTemplate], [3, "bd", bdTemplate]]
 
     for drummer, drumName, template in data:
 
         # setup the file directories
-        audioPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/audio/wet_mix/"
-        annotationPath = u"../../ENST-drums-public/drummer_" + str(drummer) + "/annotation/"
[…]
